Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-06-12 Paper/paper.tex
many new figs

\includegraphics[width=1.8\columnwidth]{plots/SingleSystemLambdaVary_q4_0_mc2_25_chi0_50}

@@

>>>>

\includegraphics[width=1.9\columnwidth]{plots/SingleSystemLambdaVary_q4_0_mc2_25_chi0_50_snr50}

@@

%%
\includegraphics[width=0.65\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr30}
\includegraphics[width=0.65\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr30}
\includegraphics[width=0.65\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr30}
\caption{\prayush{INCOMPLETE..}We illustrate here two-dimensional probability distributions, showing
the correlation between the NS tidal deformability parameter $\lambdans$ 
and binary mass and spin parameters.
\label{fig:SingleSystemLambda2DPDFs}
